Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2023-08-29 manuscript/manuscript.tex
Removed erroneous indents from codeblock
Added pandas import to codeblock

Compute the energy (\inlinecode{Eall}) and entropy (\inlinecode{dTSsix}) contributions separately.
 To make this easier, gisttool includes a function to integrate in a radius around atom centers:
\begin{lstlisting}[style=python]
	centers = {'biotin': biotin_x, 
		'strept': strept_x, 
		'compl': compl_x}
	gist_objs = {'biotin': biotin, 
		'strept': strept, 
		'compl': compl}
	cols = ['Eall_dens','dTSsix_dens']
	rmax = 12
	results = {
		name: gist.integrate_around(
		cols, rmax, centers[name])
		for name, gist in gist_objs.items()}
	display(pd.DataFrame(results))

>>>>

Compute the energy (\inlinecode{Eall}) and entropy (\inlinecode{dTSsix}) contributions separately.
 To make this easier, gisttool includes a function to integrate in a radius around atom centers:
\begin{lstlisting}[style=python]
import pandas as pd
centers = {'biotin': biotin_x, 
	'strept': strept_x, 
	'compl': compl_x}
gist_objs = {'biotin': biotin, 
	'strept': strept, 
	'compl': compl}
cols = ['Eall_dens','dTSsix_dens']
rmax = 12
results = {
	name: gist.integrate_around(
	cols, rmax, centers[name])
	for name, gist in gist_objs.items()}
display(pd.DataFrame(results))
